An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-25 article.tex
T-tests draft complete.

%We want two tables
% \ref{tab:ttests}
% \ref{fig:sigregions}
% a table for t-tests as per the f-tests table (only continuous variables)
% A map of significant areas contributing to each model.

@@

For Models 1 and 3, depicting yield and value as totals, year played a pivitol role; with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1 and 42 of 50 regions being significant in Model 3.

For Model 1, All years were significant except for the 2021/2022 financial year (where, P=4.325E-01). 32/54 giregions were significant (59.26\%). Adelaide planes was the reference region with 2012/2013 being the reference year.
%
For Model 3, all years were significant except for 2016/2017 (P=7.532E-01
). 42 out of 50 regions were significant.
% The range of how significant these variable were is important.
%
% How many were important vs how many were not?
%
% was it the same across each of the models? For example was one year/region always bad for every model?
%
\newline
With regard to continuous variables, Model 1 and 2 showed water use, scope 1 emissions and area harvested were significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed scope 1 emissions and water use to only be significant when considered as an interaction with area harvested but not when considered on their own.
\subsubsection{Model Coefficients}
% A map and a table just like the t-test section.
\begin{figure}
\caption{Violine plot of GI Region and Year coefficients for each model.}\label{fig:violin}
\includegraphics{violinplot.pdf}
\end{figure}

>>>>

@@

For Models 1 (yield) and 3 (value) year played a pivotal role, with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1, and 42 of 50 regions being significant in Model 3 with 95\% confidence.
The number of combinations of year and region meant that Models 2 and 4 had many tests (424 and 243 respectively). Model 2 found 62.56\% of these combinations were indicative of a significant contribution to the model at 95\% significance. Model 4 was found to have 88.07\% of its year/region combinations indicating a significant contribution. A likely reason for some combinations not being significant was a lack of samples in that particular region/year being present; with region sample sizes ranging from 1 to 1006.
With regard to continuous variables, Model 1 and 2 showed water use, scope 1 emissions and area harvested were significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope 1 emissions were significant. Model 4 showed scope 1 emissions and water use to only be significant when considered as an interaction with area harvested but not when considered on their own.
\subsubsection{Model Coefficients}
% A map and a table just like the t-test section.
\begin{figure}
\caption{Violine plot of GI Region and Year coefficients for each model.}\label{fig:violin}
\includegraphics{violinplot.pdf}
\end{figure}
